Cluster Difference Imaging Photometric Survey (CDIPS) II: Validatation of a Jupiter-Sized Planet in IC~2602

### 2020-06-17 paper/ms.tex
minor

\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A Validated
Jupiter-Sized Planet in IC~2602}

@@

\begin{abstract}
We present the discovery of TOI 837.01 and its validation as
a transiting planet.
We characterize the system using data from the NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA Gaia mission, ground-based photometry, and spectroscopy from CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.
We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
``Southern Pleiades''). 
The star is therefore 30$\pm$20 million years old.
The validated planet is warm ($P = 8.YY\,{\rm d}$) and roughly
  Jupiter-sized. 
However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
From TESS photometry alone, the planetary size lies within
  0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
  between the planetary size and the impact parameter of the transit.
From radial velocity monitoring, we limit the mass of planet
to less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
Grazing transits are cause for concern, as they most often are indicative of astrophysical false positive scenarios.
Our combined data render such scenarios highly unlikely.
Multi-color photometry requires eclipsing companions to be nearly the same
colors as TOI$\,$837, eliminating hierarchical eclipsing
binary scenarios.
Background eclipsing binary scenarios are limited by speckle
imaging, but formally remain a 0.2\% possibility.
TOI 837.01 therefore joins the ranks of adolescent
  exoplanets orbiting bright host stars. Further analysis of its mass,
  atmosphere, and obliquity should confirm its planetary nature beyond
  doubt, and are worthwhile because young planets do interesting
  things.
\end{abstract}

\keywords{
	Exoplanets (XXX),
	Exoplanet evolution (491),
	Stellar ages (1581),
	Young star clusters (XXX)
}

@@

>>>>

\title{
  Cluster Difference Imaging Photometric Survey (CDIPS) II:
  Validatation of a Jupiter-Sized Planet in IC~2602
}

@@

\begin{abstract}
  We present the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
  Gaia mission, ground-based photometry, and spectroscopy from
  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$20
  million years old.  The planet is warm ($P = 8.YY\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
  the planetary size and the impact parameter of the transit.  From
  radial velocity monitoring, we limit the mass of planet to less than
  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
  concern, as they usually are indicative of astrophysical false
  positive scenarios.  Our follow-up data render such scenarios highly
  unlikely.  Multi-color photometry requires eclipsing companions to
  have nearly identical color as TOI$\,$837, eliminating hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios
  are limited by speckle imaging, but formally remain a 0.2\%
  possibility.  TOI 837.01 therefore joins the ranks of adolescent
  exoplanets orbiting bright host stars as a validated planet.
  Further analysis of its mass, atmosphere, and obliquity should
  confirm its planetary nature beyond doubt, and are worthwhile
  because young planets are expected to do interesting things.
\end{abstract}

%FIXME these keywords.
\keywords{
	Exoplanets (XXX),
	Exoplanet evolution (491),
	Stellar ages (1581),
	Young star clusters (XXX)
}

@@

%TODO: pull from the cdips repo! I already wrote a lot of this...
